\section{Forums,\\ Workshops, \\ \& Symposia}

2019\hspace{.2cm}Participant, \emph{Healthy Forests, Healthy Watersheds}, Workshop, Laboratory of Tree Ring Research, University of Arizona, Tucson, AZ. November 13–15, 2019.

2019\hspace{.2cm}Organizer, \emph{Plenary Workshop — Native Waters on Arid Lands: Using wisdom from the past to guide the future of traditional practices, farming, ranching, forestry, and natural resource management}. Workshop, Fifth Annual Native Waters on Arid Lands Tribal Summit, Reno, Nevada.

2018\hspace{.2cm}Organizer, \emph{Building Research Capacity at Tribal Colleges and Universities and in Tribal Communities}. Forum, Fourth Annual Native Waters on Arid Lands Tribal Summit, Reno, Nevada.

2018\hspace{.2cm}Discussant, \emph{SKOPE: How we are making paleoenvironmental data useful and accessible}. Forum, Society for American Archaeology, 83\textsuperscript{rd} Annual Meeting, Washington, DC.

2018\hspace{.2cm}Participant, \emph{Conceptualizing a Geospatial Software Institute (GSI)}. Workshop 2: Geospatial Use Cases and Core Technical Capabilities, CyberGIS Center for Advanced Digital and Spatial Studies, Chicago, Illinois.

2017\hspace{.2cm}Guest editor, \emph{First Farmers, First Farms: Landscape Ecology of the Early Neolithic}. Edited Section, Journal of Ethnobiology.

2017\hspace{.2cm}Organizer, \emph{Traditional Knowledge \& Ecology—Building Agri-Cultural Resilience through Traditional Values}. Forum, Third Annual Native Waters on Arid Lands Tribal Summit, Reno, Nevada.

2017\hspace{.2cm}Co-organizer, \emph{Connecting Mesa Verde and the Rio Grande through the Study of Pueblo Foodways}. Forum, New Mexico History Museum, Santa Fe, New Mexico. 22 April 2017.

2017\hspace{.2cm}Discussant, \emph{Aztec at the Crossroads and in the Crosshairs: 101 Years of Research in One Convenient Symposium}. Forum, Society for American Archaeology, 82\textsuperscript{nd} Annual Meeting, Vancouver, British Columbia, Canada.

2017\hspace{.2cm}Discussant, \emph{How to do Archaeological Science using R}. Forum, Society for American Archaeology, 82\textsuperscript{nd} Annual Meeting, Vancouver, British Columbia, Canada.

2017\hspace{.2cm}Participant, \emph{Whole Tale: Computing environments for reproducibility}. Prov-a-Thon and architecture workshop, Santa Ana Pueblo, New Mexico.

2016\hspace{.2cm}Discussant, \emph{Traditional Knowledge \& Ecology}. Forum, Second Annual Native Waters on Arid Lands Tribal Summit, Las Vegas, Nevada.

2016\hspace{.2cm}Organizer, \emph{Archaeologies of Inclusion: Towards a Politics of Engagement}. Forum, Society for American Archaeology, 81\textsuperscript{st} Annual Meeting, Orlando, Florida.

2015\hspace{.2cm}Organizer, \emph{Out in the Field: Queer Experiences and Challenges in Archaeology}. Forum, Society for American Archaeology, 80\textsuperscript{th} Annual Meeting, San Francisco, California.

2014\hspace{.2cm}Discussant, \emph{Error, Sensitivity Analysis, and Uncertainty in Archaeological Computational Modeling}. Forum, Moderated by Marieka Brouwer Burg. Society for American Archaeology, 79\textsuperscript{th} Annual Meeting, Austin, Texas.

2012\hspace{.2cm}Chair, \emph{What Role did Changing Temperatures Play in the Success of North American Farming Societies in the Last Prehispanic Millennium?} Symposium, Society for American Archaeology, 77\textsuperscript{th} Annual Meeting, Memphis, Tennessee.

2011\hspace{.2cm}Participant, \emph{Graduate Workshop in Computational Social Science}. Directed by John Miller and Scott Page. Santa Fe Institute, Santa Fe, New Mexico.

2010\hspace{.2cm}Co-organizer, \emph{The Village Ecodynamics Project II}. Symposium, Society for American Archaeology, 75\textsuperscript{th} Annual Meeting, St. Louis, Missouri.
