%\newpage
\section{Outreach \& \\Press}

\emph{Sustainable Agricultural Systems in the Past, Present, and Future}
\nopagebreak
\begin{list1}
\item[] {\bf Public lecture.}
\begin{list2}
\item[-] Crow Canyon Webinar Series. 24 January 2020.

\item[-] Four Corners Lecture Series, Cortez, Colorado. Invited by the Hisatsinom Chapter of the Colorado Archaeological Society. 12 August 2019.
\end{list2}
\end{list1}

\emph{Experimental Farming: The Pueblo Farming Project and Beyond}
\nopagebreak
\begin{list1}
\item[] {\bf Public lecture.}\hspace{.2cm}In Crow Canyon Research Seminar: \emph{Connecting Mesa Verde and the Rio Grande through the Study of Pueblo Foodways}, New Mexico History Museum, Santa Fe, NM. 22 April 2017.
\end{list1}

\emph{Origins: The Journey of Humankind}
\nopagebreak
\begin{list1}
\item[] {\bf Featured expert.}\hspace{.2cm}The National Geographic Channel. Featured in Season 1, Episode 6: \emph{Building the Future}. Aired April 17, 2017. \href{https://www.natgeotv.com/int/origins-the-journey-of-humankind}{[html]}.
\end{list1}

\newpage
\emph{Farming Corn in the Past, Present, and Future}
\nopagebreak
\begin{list1}
\item[] {\bf Public lecture.}\hspace{.2cm}In Smithsonian Associates Weekend Program: \emph{Vanished! Behind the Mystery of Mesa Verde}, S. Dillon Ripley Center, Washington, DC. 21 May 2016.
\end{list1}

\emph{Exploration and exploitation in the macrohistory of the pre-Hispanic Pueblo Southwest}
\nopagebreak
\begin{list1}
\item[] {\bf Popular article}
\begin{list2}
\item[-] Do prehistoric Pueblo populist revolutions presage American politics today? Kyle Bocinsky and Tim Kohler, \emph{The Conversation}. 6 April 2016. \href{https://theconversation.com/do-prehistoric-pueblo-populist-revolutions-presage-american-politics-today-57098}{[html]}
\end{list2}

\item[] {\bf Press coverage}
\begin{list2}
\item[-] Climate and the Collapse of Ancient Civilizations. Interview on NPR's \emph{Science Friday}. 8 April 2016. \href{https://www.sciencefriday.com/segments/climate-and-the-collapse-of-ancient-civilizations/}{[html]}

\item[-] From drought, seeds of discontent. Staci Matlock, \emph{Santa Fe New Mexican}. 31 March 2016. \href{https://www.santafenewmexican.com/life/features/from-drought-seeds-of-discontent/article_8de049ea-ea1f-53a6-8444-7ba3884dc508.html}{[html]}

\item[-] Social collapse in ancient Pueblo civilization linked to climate change. Hannah Osborne, \emph{International Business Times}. 1 April 2016. \href{https://www.ibtimes.co.uk/social-collapse-ancient-pueblo-civilisation-linked-climate-change-1552706}{[html]}

\item[-] Researchers: Four Corners pueblo culture sensitive to climate. Emery Cowan, \emph{Arizona Daily Sun}, Flagstaff, Arizona. 10 April 2016. \href{https://azdailysun.com/news/local/researchers-four-corners-pueblo-culture-sensitive-to-climate/article_1703fcdd-ed87-5554-b773-19f47044dbdc.html}{[html]}
\end{list2}
\end{list1}

\emph{Can Pueblo Corn Save Ethiopian Farms? Employing 1,400 Years of Agricultural Knowledge in Service of the Future}
\nopagebreak
\begin{list1}
\item[] {\bf Public lecture}
\begin{list2}
\item[-] Southwest Seminar, Santa Fe, New Mexico. 25 July 2016.

\item[-] Arizona Archaeological and Historical Society, Tucson, Arizona. 18 January 2016.

\item[-] Four Corners Lecture Series, Cortez, Colorado. Invited by the Hisatsinom Chapter of the Colorado Archaeological Society. 4 August 2015.
\end{list2}

\end{list1}

\emph{FedData: Functions to Automate Downloading Geospatial Data Available from Several Federated Data Sources}
\nopagebreak
\begin{list1}
\item[] {\bf Blog coverage}
\begin{list2}
\item[-] Using the new R package, FedData, to access federal open datasets (including interactive graphics). \emph{ZevRoss}. 15 March 2016. \href{https://zevross.com/blog/2016/03/15/using-the-new-r-package-feddata-to-access-federal-open-datasets-including-interactive-graphics/}{[html]}
\end{list2}

\end{list1}

