%\newpage
\section{Podium \& \\Poster}


Bird, Darcy, Andrew Gillreath-Brown, {\bf R. Kyle Bocinsky}, and Tim Kohler 
\nopagebreak
\begin{list1}
\item[] 2022\hspace{.2cm}Climate, Maize, and Demography: A Case Study from the Southwestern United States. In symposium, \emph{Climatic Influences on Diet, Demography, and Conflict.} Society for American Archaeology, 87\textsuperscript{th} Annual Meeting, Chicago, Illinois.
\end{list1}

Kohler, Tim, Andrew Gillreath-Brown, {\bf R. Kyle Bocinsky}, and Darcy Bird 
\nopagebreak
\begin{list1}
\item[] 2022\hspace{.2cm}From Unconstrained to Density-dependent Growth: 900 years of Pueblo pre/history. In symposium, \emph{Demography in Archaeology beyond Boom and Bust? Critical Examination of Phases of Under- and Overpopulation.} European Association of Archaeologists, 27\textsuperscript{th} Annual Meeting, Kiel, Germany.
\end{list1}


Bird, Darcy, {\bf R. Kyle Bocinsky}, and Tim Kohler 
\nopagebreak
\begin{list1}
\item[] 2021\hspace{.2cm}Maize, Construction, and Population Changes: One Way to Identify Sunk Cost Behaviors in Central Mesa Verde. In symposium, \emph{People, Climate, and Proxies in Holocene Western North America.} Society for American Archaeology, 86\textsuperscript{th} Annual Meeting, online.
\end{list1}

Erick Robinson, Jacob Freeman, Robert L. Kelly, and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2019\hspace{.2cm}The Role of Edge Effects in Late Holocene Archaeological Radiocarbon Time Series. In symposium, \emph{Global Perspectives on Climate-Human Population Dynamics During the Late Holocene.} Society for American Archaeology, 84\textsuperscript{th} Annual Meeting, Albuquerque, New Mexico.
\end{list1}

Gillreath-Brown, Andrew, {\bf R. Kyle Bocinsky}, and Tim Kohler 
\nopagebreak
\begin{list1}
\item[] 2019\hspace{.2cm}The Impact of Temperature on the Transition to Maize Agriculture in the Northern Upland United States Southwest. In symposium, \emph{Global Perspectives on Climate-Human Population Dynamics During the Late Holocene.} Society for American Archaeology, 84\textsuperscript{th} Annual Meeting, Albuquerque, New Mexico.
\end{list1}

Glowacki, Donna, Mark Varien, Grant Coffey and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2019\hspace{.2cm}Mesa Verde Centers and Regional Analyses: Good Stuff!. In symposium, \emph{Attention to Detail: A Pragmatic Career of Research, Mentoring, and Service, Papers in Honor of Keith Kintigh.} Society for American Archaeology, 84\textsuperscript{th} Annual Meeting, Albuquerque, New Mexico.
\end{list1}

Coffey, Grant, Mark Varien and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2019\hspace{.2cm}Basketmaker III in the Central Mesa Verde Region: Transitions, Social Dynamics, and Population Growth. In symposium, \emph{Adopting the Pueblo Fettle: The Breadth and Depth of the Basketmaker III Cultural Horizon.} Society for American Archaeology, 84\textsuperscript{th} Annual Meeting, Albuquerque, New Mexico.
\end{list1}

\newpage
{\bf Bocinsky, R. Kyle}, Andrew Gillreath-Brown and Tim Kohler
\nopagebreak
\begin{list1}
\item[] 2019\hspace{.2cm}The Climates of Pueblo Emergence. In symposium, \emph{Adopting the Pueblo Fettle: The Breadth and Depth of the Basketmaker III Cultural Horizon.} Society for American Archaeology, 84\textsuperscript{th} Annual Meeting, Albuquerque, New Mexico.
\end{list1}

{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2018\hspace{.2cm}Directing the arrow by chasing its tail: Climate, adaptation, and future (agri)cultural systems in the West. In plenary symposium, \emph{Arrow of Time: Anthropological Disciplines of the Future.} 36\textsuperscript{th} Great Basin Anthropological Conference, Salt Lake City, Utah.
\end{list1}

Glowacki, Donna and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2018\hspace{.2cm}The Great Houses of the Mesa Verde Cuesta. In symposium, \emph{Mesa Verde Ancestral Pueblo Villages: Recent Research.} Society for American Archaeology, 83\textsuperscript{rd} Annual Meeting, Washington, DC.
\end{list1}

Gillreath-Brown, Andrew, {\bf R. Kyle Bocinsky}, Simon Goring and Tim A. Kohler
\nopagebreak
\begin{list1}
\item[] 2018\hspace{.2cm}Paleotemperature Reconstructions of the Upland United States Southwest for the Last 2,000 Years. In general session, \emph{Environmental Archaeology.} Society for American Archaeology, 83\textsuperscript{rd} Annual Meeting, Washington, DC.
\end{list1}

d'Alpoim Guedes, Jade, and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2017\hspace{.2cm}Climate Change, Agricultural Innovation and Exchange across Asia. American Geophysical Union, Fall Meeting 2017, New Orleans, Louisiana.
\end{list1}

{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2017\hspace{.2cm}"Constraint and Freedom" in the Era of Big Data. In Frison Institute Symposium, \emph{The Future of "Big Data" in Archaeology.} Society for American Archaeology, 82\textsuperscript{nd} Annual Meeting, Vancouver, British Columbia, Canada.
\end{list1}

Lipe, William, Laura Ellyson, {\bf R. Kyle Bocinsky}, Robin Lyle and R.G. Matson
\nopagebreak
\begin{list1}
\item[] 2017\hspace{.2cm}Costly Gobbling: Raising Turkeys in the Central Mesa Verde Area. In general session, \emph{The Archaeology of Foodways.} Society for American Archaeology, 82\textsuperscript{nd} Annual Meeting, Vancouver, British Columbia, Canada.
\end{list1}

d'Alpoim Guedes and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2017\hspace{.2cm}Modeling the Spread of Crops across Eurasia. In Fryxell Award Symposium, \emph{Papers in Honor of Naomi F. Miller.} Society for American Archaeology, 82\textsuperscript{nd} Annual Meeting, Vancouver, British Columbia, Canada.
\end{list1}

Varien, Mark. D and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2016\hspace{.2cm}The Pueblo Farming Project: Investigating the Agrarian Ecology of the Mesa Verde Region. In symposium, \emph{First Farmers, First Farms: Landscape Ecology of the Early Neolithic}. Society of Ethnobiology, 39\textsuperscript{th} Annual Conference, Tucson, Arizona.
\end{list1}

{\bf Bocinsky, R. Kyle} and Adam Brin
\nopagebreak
\begin{list1}
\item[] 2016\hspace{.2cm}SKOPE: Bringing Continent-scale, Local Paleoenvironmental Data to Researchers and the Public. In symposium, \emph{What Do We Mean by "Digital Curation?"} Society for American Archaeology, 81\textsuperscript{st} Annual Meeting, Orlando, Florida.
\end{list1}

d'Alpoim Guedes, Jade, Sturt Manning, and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2016\hspace{.2cm}5500 Years of Changing Crop Niches on the Tibetan Plateau. In symposium, \emph{Guava Cat Archaeology: Papers in Memory of Prof. Pochan Chen.} Society for American Archaeology, 81\textsuperscript{st} Annual Meeting, Orlando, Florida.
\end{list1}

\newpage
Ellyson, Laura, Timothy Kohler, and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2016\hspace{.2cm}Evaluation of the Village Ecodynamics Hunting and Domestication Models. In general session, \emph{Southwestern Archaeology.} Society for American Archaeology, 81\textsuperscript{st} Annual Meeting, Orlando, Florida.
\end{list1}

Van Dyke, Ruth M., {\bf R. Kyle Bocinsky}, Tucker Robinson, and Thomas C. Windes
\begin{list1}
\item[] 2016\hspace{.2cm}{Great houses, shrines, and high places: Intervisibility across the Chacoan World}. 2016 Navajo Nation Archaeology Meeting, Shiprock, New Mexico. 4 March 2016.
\end{list1}

{\bf Bocinsky, R. Kyle}, Jade d'Alpoim Guedes, Karen Adams, Rob Quinlan, Mark Caudell, and Timothy A. Kohler
\nopagebreak
\begin{list1}
\item[] 2016\hspace{.2cm}Can Pueblo Corn Save Ethiopian Farms?  Deploying 1,400 Years of Agricultural Knowledge in Service of the Future.  In symposium, \emph{Engaged Archaeology through Transnational, Interdisciplinary, and Indigenous Collaborations.}15\textsuperscript{th} Biennial Southwest Symposium, Tucson, Arizona.
\end{list1}

Schwindt, Dylan M., {\bf R. Kyle Bocinsky}, Scott G. Ortman, Donna M. Glowacki, Mark D. Varien, and Timothy A. Kohler
\nopagebreak
\begin{list1}
\item[] 2016\hspace{.2cm}Interactions among society, climate, production, and population: A case study from the central Mesa Verde region with contemporary implications. In symposium, \emph{Engaged Archaeology through Transnational, Interdisciplinary, and Indigenous Collaborations.}15\textsuperscript{th} Biennial Southwest Symposium, Tucson, Arizona.
\end{list1}

{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2015\hspace{.2cm}What is the Pecos System, Anyway? 2015 Pecos Conference, Mancos, Colorado. Winner of the 2015 Cordell Prize.
\end{list1}


{\bf Bocinsky, R. Kyle}, Keith Kintigh, Timothy Kohler, Bertram Lud\"ascher, Ann Kinzig, Carla Van West, Margaret Nelson, Adam Brin, Sarah Oas, Johnathan Rush, Timothy McPhillips, and Yang Cao
\nopagebreak
\begin{list1}
\item[] 2015\hspace{.2cm}Toward Effective Cyber-Infrastructure Support of Socio-Environmental Research. In symposium, \emph{The Robustness and Vulnerability of Food Production and Social Change: An Evaluation of Interdisciplinary Concepts Using Archaeological Data, Models, and Ethnographic Observations.} Society for American Archaeology, 80\textsuperscript{th} Annual Meeting, San Francisco, California.
\end{list1}


Van Dyke, Ruth, {\bf R. Kyle Bocinsky}, and Tucker Robinson
\nopagebreak
\begin{list1}
\item[] 2015\hspace{.2cm}Friends in High Places: Windes, Shrines, and Lines of Sight. In symposium, \emph{It's About Time: Contributions in Honor of Thomas C. Windes.} Society for American Archaeology, 80\textsuperscript{th} Annual Meeting, San Francisco, California.
\end{list1}


Kohler, Timothy A., Stefani A. Crabtree, and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2015\hspace{.2cm}The Effects of Temporal Coarse-Graining on Inferred Networks of Human Movement. In symposium, \emph{The Short and Long of It: Combining Timescales.} Society for American Archaeology, 80\textsuperscript{th} Annual Meeting, San Francisco, California.
\end{list1}


Crabtree, Stefani A., {\bf R. Kyle Bocinsky}, and Timothy A. Kohler
\nopagebreak
\begin{list1}
\item[] 2015\hspace{.2cm}Alliances, Coalitions, Hierarchies and Conflict in the AncestralPueblo World. In symposium, \emph{Simulating Social Complexity to Understand the Archaeological Past.} Society for American Archaeology, 80\textsuperscript{th} Annual Meeting, San Francisco, California.
\end{list1}


McPhillips, Timothy, Tianhong Song, Tyler Kolisnik, Steve Aulenbach, Khalid Belhajjame, {\bf R. Kyle Bocinsky}, Yang Cao, Fernando Chiriga, Saumen Dey, Juliana Freire, Deborah Huntzinger, Christopher Jones, David Koop, Paolo Missier, Mark Schildhauer, Christopher Schwalm, Yaxing Wei, James Cheney, Mark Bieda, and Bertram Lud\"ascher
\nopagebreak
\begin{list1}
\item[] 2015\hspace{.2cm}YesWorkflow: A User-Oriented, Language-Independent Tool for Recovering Workflow Information from Scripts. 10\textsuperscript{th} International Digital Curation Conference, London.
\end{list1}

\newpage
Crabtree, Stefani A., {\bf R. Kyle Bocinsky}, and Timothy A. Kohler
\nopagebreak
\begin{list1}
\item[] 2014\hspace{.2cm}Modeling Emergence of Complex Groups on Realistic Landscapes. In symposium, \emph{Principles of Complexity: Life, Scale, and Civilization III.} Santa Fe Institute, Santa Fe, New Mexico. August.
\end{list1}


{\bf Bocinsky, R. Kyle}, Kurt F. Anscheutz, Jesse Clark, and Timothy A. Kohler
\nopagebreak
\begin{list1}
\item[] 2014\hspace{.2cm}A General Spatial Reconstruction of Potential Maize Paleoproductivity, AD 600–2000. In symposium, \emph{Coupled Regions, Coupled Systems: Dynamics of Prehispanic Farming Societies in the Northern San Juan and the Northern Rio Grande.} Society for American Archaeology, 79\textsuperscript{th} Annual Meeting, Austin, Texas.
\end{list1}


Kohler, Timothy A., Kelsey M. Reese, Stefani A. Crabtree, {\bf R. Kyle Bocinsky}, and Brian M. Kemp
\nopagebreak
\begin{list1}
\item[] 2014\hspace{.2cm}Prolegomenon: VEP II, Almost in Retrospect. In symposium, \emph{Coupled Regions, Coupled Systems: Dynamics of Prehispanic Farming Societies in the Northern San Juan and the Northern Rio Grande.} Society for American Archaeology, 79\textsuperscript{th} Annual Meeting, Austin, Texas.
\end{list1}


Crabtree, Stefani A., Timothy A. Kohler and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2014\hspace{.2cm}The Development of Social Groups, Leadership and Inequality in the Central Mesa Verde. \emph{In symposium, Coupled Regions, Coupled Systems: Dynamics of Prehispanic Farming Societies in the Northern San Juan and the Northern Rio Grande.} Society for American Archaeology, 79\textsuperscript{th} Annual Meeting, Austin, Texas.
\end{list1}


Conway, Meagan and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2014\hspace{.2cm}Household and Community Scales of
Post-Famine Demographic Change in Western Ireland. In symposium, \emph{The Archaeology of the Irish Famine: Exploring Lasting Effects on Local, Regional, and Transatlantic Scales.} Society for American Archaeology, 79\textsuperscript{th} Annual Meeting, Austin, Texas.
\end{list1}


{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2013\hspace{.2cm}Pueblo II and the Turkey Taboo: Changing Attitudes Towards Domesticated Turkeys in the Puebloan Southwest. In symposium, \emph{Food: It's What's for Dinner.} American Anthropological Association, 2013 Annual Meeting, Chicago, Illinois.
\end{list1}


Kohler, Timothy A., {\bf R. Kyle Bocinsky}, Stefani A. Crabtree, Andrew Hlynka, Lokesh Patil, Paul Lovell Hooper and Ziad Kobti
\nopagebreak
\begin{list1}
\item[] 2013\hspace{.2cm}Leadership, Territoriality and Conflict in an Agentized Pueblo World. In symposium, \emph{Complex-systems Approaches to Long-term Change.} American Anthropological Association, 2013 Annual Meeting, Chicago, Illinois.
\end{list1}


{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2013\hspace{.2cm}"Free nights and weekends" in the AD 1000s? 
Prehistoric visual communication systems and the influence of infrastructure on modern social network formation. In lecture series, \emph{Reckless Ideas.} Santa Fe Institute, Santa Fe, New Mexico. August 23, 2013.
\end{list1}


{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2013\hspace{.2cm}The Data Are the Context: A Student's Perspective on the Colorado Contexts, Old and New. In symposium, \emph{Updating the 1999 Colorado Prehistoric Contexts: How a Digital Research Context for Southwestern Colorado Could Be Organized and Assembled.} Colorado Council of Professional Archaeologists, 35th Annual Conference, Denver, Colorado.
\end{list1}


{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2013\hspace{.2cm}The Defensive Coast. In general session, \emph{Landscapes and Spatial Analysis: Global Case Studies.} Society for American Archaeology, 78\textsuperscript{th} Annual Meeting, Honolulu, Hawaii. Winner of the 2013 R.E. Taylor Student Poster Award from the Society for Archaeological Sciences. %\href{http://village.anth.wsu.edu/sites/village.anth.wsu.edu/files/publications/BOCINSKY_NW_Defense_10.pdf}{[pdf]}
\end{list1}


Reese, Kelsey M., {\bf R. Kyle Bocinsky}, Donna M. Glowacki, Scott G. Ortman and Timothy A. Kohler
\nopagebreak
\begin{list1}
\item[] 2013\hspace{.2cm}What Are Communities, Really? In symposium, \emph{New Directions in Modeling Dynamics for Coupled Social-Natural Systems.} Society for American Archaeology, 78\textsuperscript{th} Annual Meeting, Honolulu, Hawaii.
\end{list1}


{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2013\hspace{.2cm}Why Landscapes Matter: Inferring Defensiveness around the Salish Sea. In symposium, \emph{Why Salish Sea Archaeology Matters: Current Perspectives from Washington State University.} 66\textsuperscript{th} Annual Northwest Anthropological Conference, Portland, Oregon.
\end{list1}


{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2012\hspace{.2cm}Simulating Archaeological Landscapes using the RePAST Agent Based Modeling Framework. In invited colloquium, Institute of Archaeology and Museology, Faculty of Arts, Masaryk University, Brno, Czech Republic.
\end{list1}


{\bf Bocinsky, R. Kyle} and Timothy A. Kohler
\nopagebreak
\begin{list1}
\item[] 2012\hspace{.2cm}Suboptimal Foraging Theory (It's the Best). In symposium, \emph{Socionatural Systems in the Northern U.S. Southwest: A Village Ecodynamics Project II Progress Report.} Society for American Archaeology, 77\textsuperscript{th} Annual Meeting, Memphis, Tennessee.
\end{list1}


Kohler, Timothy A. and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2012\hspace{.2cm}Highly Variable Temperatures in the Northern Hemisphere over the Last Two Millennia: Reconstructions and Possible Effects on Native American Agricultural Systems. In symposium, \emph{What Role did Changing Temperatures Play in the Success of North American Farming Societies in the Last Prehispanic Millennium?} Society for American Archaeology, 77\textsuperscript{th} Annual Meeting, Memphis, Tennessee.
\end{list1}


Newbold, Bradley, {\bf R. Kyle Bocinsky}, William D. Lipe, Phil R. Geib and Brian M. Kemp
\nopagebreak
\begin{list1}
\item[] 2012\hspace{.2cm}Revising Early Turkey Domestication in the Southwest. In general session, \emph{Archaeology of the Ancestral Puebloans and Paquime.} Society for American Archaeology, 77\textsuperscript{th} Annual Meeting, Memphis, Tennessee.
\end{list1}


Reese, Kelsey M., {\bf R. Kyle Bocinsky}, Kay E. Barnett, Stefani A. Crabtree and Elise Alonzi
\nopagebreak
\begin{list1}
\item[] 2012\hspace{.2cm}Large, Aggregated Villages in Little Soda Canyon. In general session, \emph{Southwest.} Society for American Archaeology, 77\textsuperscript{th} Annual Meeting, Memphis, Tennessee. %\href{http://village.anth.wsu.edu/sites/village.anth.wsu.edu/files/publications/bocinsky_thesis_final.pdf}{[pdf]}
\end{list1}


{\bf Bocinsky, R. Kyle} and Timothy A. Kohler
\nopagebreak
\begin{list1}
\item[] 2011\hspace{.2cm}Toward [Re]Constructing An Archaeological Legacy of Hunting On the Colorado Plateau. In Evolutionary Anthropology Society invited symposium, \emph{Lasting Legacies and Changing Tides in Human Behavioral Ecology.} American Anthropological Association, 2011 Annual Meeting, Montreal, Quebec, Canada.
\end{list1}


{\bf Bocinsky, R. Kyle}, Brian Chisholm and Brian M. Kemp
\nopagebreak
\begin{list1}
\item[] 2011\hspace{.2cm}Basketmaker III Turkey Use: Multiple Lines of Evidence. In symposium, \emph{The Cedar Mesa Project Turns 40: New Results from a Long-Lived Study in SE Utah.} Society for American Archaeology, 76\textsuperscript{th} Annual Meeting, Sacramento, California.
\end{list1}


Newbold, Bradley, {\bf R. Kyle Bocinsky}, Brian M. Kemp and Phil R. Geib
\nopagebreak
\begin{list1}
\item[] 2011\hspace{.2cm}Ancient Domestic Turkeys at Atlatl Rock Cave. In general session, \emph{Animal Domesticates in the Americas.} Society for American Archaeology, 76\textsuperscript{th} Annual Meeting, Sacramento, California.
\end{list1}


Crabtree, Stefani A., Ziad Kobti, Timothy A. Kohler and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2011\hspace{.2cm}Archaeology Time Machine: Witnessing Social Interactions on the Pueblo Landscape through Agent-based Simulation. In symposium, \emph{Mapping and Technological Experiments in Archaeology.} Society for American Archaeology, 76\textsuperscript{th} Annual Meeting, Sacramento, California.
\end{list1}


Kohler, Timothy A., {\bf R. Kyle Bocinsky}, Stefani A. Crabtree and Denton Cockburn
\nopagebreak
\begin{list1}
\item[] 2011\hspace{.2cm}The Village Ecodynamics Project: Modeling the Deep Pueblo Past. In symposium, \emph{Modeling Across Millennia: Interdisciplinary Paths to Ancient Socionatural Systems.} 177\textsuperscript{th} AAAS Annual Meeting, Washington, D.C.
\end{list1}

\newpage
Barron, Doug, {\bf R. Kyle Bocinsky}, Dan Grunspan, Bradley Newbold, Darryl Trumbo and Bryan \\Roosien
\nopagebreak
\begin{list1}
\item[] 2011\hspace{.2cm}Mapping the Memetics Meme: Toward a better understanding of the transmission and evolution of scientific concepts. In IGERT Program in Evolutionary Modeling seminar, Washington State University, Pullman, Washington.
\end{list1}


Barron, Doug, {\bf R. Kyle Bocinsky}, Dan Grunspan, Bradley Newbold, Darryl Trumbo and Bryan \\Roosien
\nopagebreak
\begin{list1}
\item[] 2010\hspace{.2cm}GroupAge: An agent-based framework for exploring the interaction of social learning, mate choice, and group dynamics. In IGERT Program in Evolutionary Modeling seminar, Washington State University, Pullman, Washington.
\end{list1}


{\bf Bocinsky, R. Kyle}, Breanne M. Nott and Brian M. Kemp
\nopagebreak
\begin{list1}
\item[] 2010\hspace{.2cm}Plop! Jump-starting the brown revolution in archaeology. In symposium, \emph{The Village Ecodynamics Project II.} Society for American Archaeology, 75\textsuperscript{th} Annual Meeting, St. Louis, Missouri.
\end{list1}


Glowacki, Donna M., Charles A. Reed, {\bf R. Kyle Bocinsky}, Shanna Diederichs and Julie Bell
\nopagebreak
\begin{list1}
\item[] 2010\hspace{.2cm}Making sense of the actual: Settlement trends in the southwestern Colorado VEP study areas. In symposium, \emph{The Village Ecodynamics Project II.} Society for American Archaeology, 75\textsuperscript{th} Annual Meeting, St. Louis, Missouri.
\end{list1}


Reed, Charles A., Ryan Lash and {\bf R. Kyle Bocinsky}
\nopagebreak
\begin{list1}
\item[] 2010\hspace{.2cm}An Ancestral Puebloan Community in Morefield Canyon, Mesa Verde National Park. In general session, \emph{What's New in Southwestern Archaeology?} Society for American Archaeology, 75\textsuperscript{th} Annual Meeting, St. Louis, Missouri. %\href{http://village.anth.wsu.edu/sites/village.anth.wsu.edu/files/publications/ReedLashBocinsky_compressed.pdf}{[pdf]}
\end{list1}


{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2009\hspace{.2cm}In the land of plenty: Agent-based approaches to modeling subsistence in the Puebloan Southwest. In South Carolina Institute of Archaeology and Anthropology seminar, \emph{From Field to Table: Historical Ecology of Regional Subsistence Strategies}. University of South Carolina, Columbia, South Carolina.
\end{list1}


{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2009\hspace{.2cm}Village Evolving: New directions in VEP research. In NSF Office of Polar Programs: Arctic Social Sciences sponsored conference, \emph{Global Long Term Human Ecodynamics}. Eagle Hill, Maine.
\end{list1}


{\bf Bocinsky, R. Kyle}
\nopagebreak
\begin{list1}
\item[] 2009\hspace{.2cm}Understanding and modeling turkey use in the American Southwest: A preliminary simulation module for RePAST. In general session, \emph{General New World and Methods.} Society for American Archaeology, 74\textsuperscript{th} Annual Meeting, Atlanta, Georgia. %\href{http://village.anth.wsu.edu/sites/village.anth.wsu.edu/files/publications/BocinskySAA09Poster.pdf}{[pdf]}
\end{list1}


{\bf Bocinsky, R. Kyle}, Terrence Martin and Mark A. Schurr
\nopagebreak
\begin{list1}
\item[] 2008\hspace{.2cm}Rodent Stable Carbon-isotope Ratios as a Measure of Maize Production. In general session, \emph{Methods and Advances in Zooarchaeology.} Society for American Archaeology, 73\textsuperscript{rd} Annual Meeting, Vancouver, British Columbia, Canada. %\href{http://village.anth.wsu.edu/sites/village.anth.wsu.edu/files/publications/BocinskySAA\%202008.pdf}{[pdf]}
\end{list1}

