\section{Book \\ Contributions \\ \normalsize{$^\ast$ peer-reviewed}}

$^\ast$ Schachner, Gregson, Joel Nicholas, R. J. Sinensky, and {\bf R. Kyle Bocinsky}
\begin{list1}
\item[] 2021\hspace{.2cm}{The sustainability of Hopi agriculture}. In \emph{Becoming Hopi: A History}, edited by Wesley Bernardini, Stewart Koyiyumptewa, Gregson Schachner, and Leigh Kuwanwisiwma, pp. 113–132. University of Arizona Press, Tucson.\\\href{https://uapress.arizona.edu/book/becoming-hopi}{https://uapress.arizona.edu/book/becoming-hopi}
	\\\bf\emph{Winner of the 2022 Society for American Archaeology Scholarly Book Award.}
\end{list1}


$^\ast$ Van Dyke, Ruth M., Timothy De Smet, and {\bf R. Kyle Bocinsky}
\begin{list1}
\item[] 2021\hspace{.2cm}{Viewscapes and Soundscapes}. In \emph{The Greater Chaco Landscape: Ancestors, Scholarship, and Advocacy}, edited by Ruth Van Dyke and Carrie Heitman, Chapter 11. University Press of Colorado, Boulder.\\\href{http://read.upcolorado.com/projects/the-greater-chaco-landscape}{http://read.upcolorado.com/projects/the-greater-chaco-landscape}
	\\\bf\emph{Winner of the 2022 Society for American Archaeology Popular Book Award.}

\end{list1}


$^\ast$ Kohler, Timothy A., Laura J. Ellyson and {\bf R. Kyle Bocinsky}
\begin{list1}
\item[] 2020\hspace{.2cm}{Beyond One-Shot Hypotheses: Explaining Three Increasingly Large Collapses in the Northern Pueblo Southwest}. In \emph{Going forward by Looking Back: Archaeological Perspectives on Socio-Ecological Crisis, Response and Collapse}, edited by Felix Reide and Payson Sheets, pp. 304–332. Berghahn Books, New York.\\\href{https://www.berghahnbooks.com/title/RiedeGoing}{https://www.berghahnbooks.com/title/RiedeGoing}
\end{list1}


Ermigiotti, Paul, Mark Varien, Erin Bohm, {\bf Kyle Bocinsky}, the Hopi Cultural Preservation Office, and the Hopi Cultural Resources Advisory Task Team 
\begin{list1}
\item[] 2018\hspace{.2cm}{\emph{The Pueblo Farming Project: A collaboration between Hopi farmers and the Crow Canyon Archaeological Center}}. Crow Canyon Archaeological Center, Cortez, Colorado.\\\href{https://pfp.crowcanyon.org}{https://pfp.crowcanyon.org}
\end{list1}

\newpage
$^\ast$ Kohler, Timothy A., Stefani A. Crabtree, {\bf R. Kyle Bocinsky}, and Paul L. Hooper 
\begin{list1}
\item[] 2018\hspace{.2cm}{Sociopolitical Evolution in Midrange Societies: The Prehispanic Pueblo Case}. In \emph{The Emergence of Premodern States: New Perspectives on the Development of Complex Societies}, edited by Jeremy A. Sabloff and Paula L.W. Sabloff, pp. 133–186. SFI Press, Santa Fe, New Mexico.\\\href{https://www.sfipress.org/books/emergence-of-premodern-states}{https://www.sfipress.org/books/emergence-of-premodern-states}
\end{list1}


$^\ast$ Kohler, Timothy A. and {\bf R. Kyle Bocinsky}
\begin{list1}
\item[] 2017\hspace{.2cm}Crises as opportunities for culture change. In \emph{Crisis to Collapse: The Archaeology of Social Breakdown}, edited by Tim Cunningham and Jan Driessen, pp. 263–273. Presses Universitaires de Louvain, Louvain, France.\\\href{https://pul.uclouvain.be/book/?GCOI=29303100293170}{https://pul.uclouvain.be/book/?GCOI=29303100293170}
\end{list1}

$^\ast$ {\bf Bocinsky, R. Kyle} and Timothy A. Kohler
\begin{list1}
\item[] 2016\hspace{.2cm}Complexity, rigidity, and resilience in the Ancient Puebloan Southwest. In \emph{Viewing the Future in the Past: Historical Ecology Applications to Environmental Issues}, edited by H. Thomas Foster, II, Lisa Paciulli, and David Goldstein. pp. 86–105. University of South Carolina Press, Columbia, South Carolina.\\\href{https://uscpress.com/Viewing-the-Future-in-the-Past}{https://uscpress.com/Viewing-the-Future-in-the-Past}
\end{list1}


$^\ast$ {\bf Bocinsky, R. Kyle}, Jason A. Cowan, Timothy A. Kohler and C. David Johnson
\begin{list1}
\item[] 2012\hspace{.2cm}Hunting results: How hunting changes the VEP world, and how the VEP world changes hunting. In \emph{Emergence and Collapse of Early Villages: Models of Central Mesa Verde Archaeology}, edited by T.A. Kohler, and M.D. Varien, pp. 145–152. University of California Press, Berkeley.\\\href{https://www.ucpress.edu/ebook/9780520951990/emergence-and-collapse-of-early-villages}{https://www.ucpress.edu/ebook/9780520951990/emergence-and-collapse-of-early-villages}
\end{list1}


$^\ast$ Kohler, Timothy A., {\bf R. Kyle Bocinsky}, Stefani A. Crabtree and Ben Ford
\begin{list1}
\item[] 2012\hspace{.2cm}Supply, Demand, Return Rates, and Resource Depression: Hunting in the Village
Ecodynamics World. In \emph{Emergence and Collapse of Early Villages: Models of Central Mesa Verde Archaeology}, edited by T.A. Kohler, and M.D. Varien, pp. 129–144. University of California Press, Berkeley.\\\href{https://www.ucpress.edu/ebook/9780520951990/emergence-and-collapse-of-early-villages}{https://www.ucpress.edu/ebook/9780520951990/emergence-and-collapse-of-early-villages}
\end{list1}


$^\ast$ Cowan, Jason A., Timothy A. Kohler, C. David Johnson, Kevin Cooper and {\bf R. Kyle Bocinsky}
\begin{list1}
\item[] 2012\hspace{.2cm}Exercising the Model: Settlement Efficiency and Changes in Locational Practice. In \emph{Emergence and Collapse of Early Villages: Models of Central Mesa Verde Archaeology}, edited by T.A. Kohler, and M.D. Varien, pp. 153–164. University of California Press, Berkeley.\\\href{https://www.ucpress.edu/ebook/9780520951990/emergence-and-collapse-of-early-villages}{https://www.ucpress.edu/ebook/9780520951990/emergence-and-collapse-of-early-villages}
\end{list1}
