\section{Technical Reports}

{\bf Bocinsky, R. Kyle}
\begin{list1}
\item[] 2020\hspace{.2cm}Defining Accurate Floating Coordinate Reference Systems for Legacy Crow Canyon Projects. Crow Canyon Archaeological Center, Cortez, Colorado. \\\href{https://crowcanyon.github.io/localgrid/articles/floating-grid-trigonometry.html}{https://crowcanyon.github.io/localgrid/articles/floating-grid-trigonometry.html}
\end{list1}


Glowacki, Donna M., {\bf R. Kyle Bocinsky}, Kelsey M. Reese, and Katherine A. Portman
\begin{list1}
\item[] 2017\hspace{.2cm}The Mesa Verde Community Center Survey: Summer 2017. Manuscript submitted to Mesa Verde National Park, on file with Crow Canyon Archaeological Center and the University of Notre Dame.
\end{list1}


Glowacki, Donna M., with contributions by Elise Alonzi, {\bf R. Kyle Bocinsky}, and Kelsey Reese
\begin{list1}
\item[] 2012\hspace{.2cm}The Mesa Verde Community Center Survey: Final Report. Manuscript submitted to the National Science Foundation and Mesa Verde National Park, on file with Crow Canyon Archaeological Center and Washington State University in compliance with deliverable for NSF Grant DEB-0816400.%\\\href{http://village.anth.wsu.edu/sites/village.anth.wsu.edu/files/publications/FINAL_REPORT_VEP_2012_noUTMs.pdf}{[pdf]}
\end{list1}


Glowacki, Donna M. and {\bf R. Kyle Bocinsky}
\begin{list1}
\item[] 2011\hspace{.2cm}The Mesa Verde Community Center Survey: 2011 Progress Report. Manuscript submitted to the National Science Foundation and Mesa Verde National Park, on file with Crow Canyon Archaeological Center and Washington State University in compliance with deliverable for NSF Grant DEB-0816400.%\\\href{http://village.anth.wsu.edu/sites/village.anth.wsu.edu/files/publications/MVCCS2011_report_no_UTMs.pdf}{[pdf]}
\end{list1}


Reed, Charles A., {\bf R. Kyle Bocinsky} and Donna M. Glowacki
\begin{list1}
\item[] 2009\hspace{.2cm}Mesa Verde National Park Community Center Survey: Report and Synthesis. Manuscript submitted to the National Science Foundation and Mesa Verde National Park, on file with Crow Canyon Archaeological Center and Washington State University in compliance with deliverable for NSF Grant DEB-0816400.
\end{list1}
